Analysis

### 2023-04-24 analysis/analysis.Rmd
Refactor maps in analysis
Removing external/online dependencies: webshot, magick, natural earth data (now in raw_data), stamen

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!webshot::is_phantomjs_installed()) webshot::install_phantomjs()
library(magick)
```

@@

```{r message=FALSE}
library(tidyverse)
library(ggdist)
library(reshape2)
library(here)
library(RcppRoll)
library(sf)
library(mapview)
library(vegan)
library(neotoma)
library(analogue)
library(rcarbon)
library(doParallel)
library(nimble)
library(coda)
library(MCMCvis)
library(fmcmc)
```

@@

@@

```{r}
pollen_locations.sf <- st_as_sf(pollen_locations,
                                coords = c("lng", "lat"), # coordinate columns
                                crs = 4326)  # coordinate references system in epsg))
pollen_locations.sf.lv95 <- st_transform(pollen_locations.sf, crs = 2056)

pollenmap <- tempfile(fileext = ".png")
mapshot(
  mapview(pollen_locations.sf),
  file = pollenmap
  )

img <- magick::image_read(pollenmap)
old.par <- par(mar = c(0, 0, 0, 0))
plot(img)
par(old.par)
```

@@

```{r}
c14map <- tempfile(fileext = ".png")
mapshot(
  mapview(st_as_sf(c14,
                   coords = c("lng", "lat"), 
                   crs = 4326),layer.name = "14C Data"
          ),
  file = c14map
  )

img <- magick::image_read(c14map)
old.par <- par(mar = c(0, 0, 0, 0))
plot(img)
par(old.par)
```

@@

```{r}
sitesmap <- tempfile(fileext = ".png")
mapshot(
  mapview(st_as_sf(sites,
                   coords = c("LV03_Rechtswert_fuzzy", "LV03_Hochwert_fuzzy"),
                   crs = 21781),
          layer.name = "Sites"
  ),
  file = sitesmap
)
img <- magick::image_read(sitesmap)
old.par <- par(mar = c(0, 0, 0, 0))
plot(img)
par(old.par)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r message=FALSE}
library(tidyverse)
library(ggdist)
library(reshape2)
library(here)
library(RcppRoll)
library(sf)
library(ggspatial)
library(vegan)
library(neotoma)
library(analogue)
library(rcarbon)
library(doParallel)
library(nimble)
library(coda)
library(MCMCvis)
library(fmcmc)
```

@@

```{r}
source(here("code/map_helpers.R"))
```

@@

```{r}
pollen_locations.sf <- st_as_sf(pollen_locations, 
                                coords = c("lng", "lat"), crs = 4326)

base_map() + 
  geom_sf(data = pollen_locations.sf, inherit.aes = FALSE) +
  base_coord()
```

@@

```{r}
c14.sf <- c14 |>
  distinct(site, lat, lng) |>
  st_as_sf(coords = c("lng", "lat"),  crs = 4326)

base_map() +
  layer_spatial(c14.sf) +
  base_coord()
```

@@

```{r}
sites.sf <- st_as_sf(sites,
                   coords = c("LV03_Rechtswert_fuzzy", "LV03_Hochwert_fuzzy"),
                   crs = 21781)

base_map() + 
  layer_spatial(sites.sf) +
  base_coord()
```
